Peptide retention time prediction

### 2014-11-08 retention.tex
Added a paragraph about Elude and a table listing rt methods

\documentclass[a4paper]{article}
\usepackage{graphicx}
\usepackage{wrapfig}

@@

Following these observations, a variety of retention time prediction
methods has been proposed. These methods can be roughly divided into
three classes: index-based methods, modeling-based techniques and
machine learning approaches. The main ideas underlying each category
are described below.

@@

@@

>>>>

\documentclass[a4paper]{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{url}
\usepackage{multirow}

@@

Following these observations, a variety of retention time prediction
methods has been proposed. These methods can be roughly divided into
three classes: index-based methods, modeling-based techniques and
machine learning approaches. The main ideas underlying each category
are described below, while Table \ref{tab:rtmethods} lists a few of the most popular retention time 
prediction methods from each category.

@@

In our group we developed a software package which we named {\sc
Elude} \cite{elude1, elude2}. One of the main novelty
points of {\sc Elude} is the calculation of peptide features based on
both a general hydrophobicity index, as well as a retention index
trained for each dataset at hand. This ensures that the algorithm
can be applied to different chromatography setups with minimal loss
in performance. For cases when little training data is available,
{\sc ELUDE} implements an additional workflow based on a library of
pre-trained retention models. This workflow requires only a few tens
of training peptides to select and calibrate the most suitable model
from the library. Both the selection and calibration are performed
using statistical methods robust to outliers.

@@

\begin{table}
 \caption{{\bf Retention time prediction methods.} We
   give a few of the most commonly used retention time prediction methods available.}
 \vspace{.2cm}
 \label{tab:rtmethods}
 \begin{tabular}{lll}

 Method name & Link & Reference  \\
 \hline
SSRCalc & \url{http://hs2.proteome.ca/SSRCalc/SSRCalcX.html} & [\cite{Krokhin2004}, \cite{Krokhin2006}, \cite{Spicer2007}] \\
BioLCCC & \url{http://theorchromo.ru/} & [\cite{gorshkov2006}] \\
ANN & Link? & [\cite{petritis2003}, \cite{petritis2006improved}] \\
RTModel, RTPredict &  \url{http://ftp.mi.fu-berlin.de/OpenMS/documentation/html/TOPP_RTPredict.html}, 
 & [\cite{rtpredict}, \cite{rtpredictImproved}] \\
&\url{http://ftp.mi.fu-berlin.de/OpenMS/documentation/html/TOPP_RTModel.html}  & \\

Elude & \url{http://elude.sbc.su.se/} & [\cite{elude1}, \cite{elude2}] \\
\hline
 \end{tabular} \\
\end{table}
